Safety Analysis of the Molten Salt Fast Reactor Fuel Composition using Moltres

### 2019-08-01 paper/paper.tex
Review edits

\title{SAFETY ANALYSIS OF THE MOLTEN SALT FAST REACTOR FUEL COMPOSITION USING
MOLTRES \\~\\~\\~\\}
\author{Sun Myung Park$^{a,b}$, Andrei Rykhlevskii$^a$, and
Kathryn D. Huff$^a$}
\institute{$^a$Dept. of Nuclear, Plasma and Radiological Engineering,
University of Illinois at Urbana-Champaign \\
$^b$smpark3@illinois.edu}

\usepackage{graphicx} % allows inclusion of graphics
\usepackage{booktabs} % nice rules (thick lines) for tables
\usepackage{microtype} % improves typography for PDF
\usepackage{float}
\usepackage{longtable}
\usepackage{xspace}
\usepackage{multirow} 
\usepackage{array}
\setlength{\arrayrulewidth}{.4mm}
\renewcommand{\arraystretch}{1.2}
\usepackage[labelfont=bf]{caption}
%\captionsetup[table]{name=Table}
\renewcommand{\thetable}{\arabic{table}}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{enumitem}
\usepackage{placeins}
\usepackage{siunitx}
\newcolumntype{c}{>{\hsize=.56\hsize}X}
\newcolumntype{b}{>{\hsize=.7\hsize}X}
%\newcolumntype{s}{>{\hsize=.74\hsize}X}
\newcolumntype{f}{>{\hsize=.1\hsize}X}
\newcolumntype{a}{>{\hsize=.45\hsize}X}
%\usepackage{titlesec}
%\titleformat*{\subsection}{\normalfont}
%\usepackage[super]{cite}
\usepackage{multirow}
\usepackage{hhline}

@@

\begin{abstract}
%
\textit{
    The Molten
    Salt Fast Reactor (MSFR) has garnered much interest for its inherent
    safety and sustainbility features. The MSFR can adopt a closed thorium fuel
    cycle for
    sustainable operation through the breeding of $^{233}$U from $^{232}$Th.
    The fuel composition changes significantly over the course of its lifespan.
    In this study, we investigated the steady state and transient behavior of
    the MSFR using Moltres, a coupled neutronics/thermal-hydraulics code
    developed within the Multiphysics Object Oriented Simulation Environment
    (MOOSE) framework. Three different fuel compositions, start-up,
    early-life, and equilibrium, were examined for potentially
    dangerous
    core temperature excursions during a unprotected loss of heat sink (ULOHS)
    accident. The steady state peak neutron flux showed good agreement
    with existing MSFR data, while the temperature distribution and total power
    showed discrepancies which can be attributed to known sources of error.
    For the transient behavior under the ULOHS
    scenario, while the transition time towards the new steady state core
    temperature is also in good agreement with existing MSFR simulations by
    Fiorina et al., Moltres underestimated the
    temperature rise by a factor of ten, due to the same sources of
    error for the steady state results. While an MSFR loaded with
    start-up fuel composition operates at a higher temperature than with the
    other two fuel compositions, all three cases were shown to be inherently
    safe due to the strong negative temperature feedback.
}
\end{abstract}

@@

    We generated group constants for 
    each fuel composition using SERPENT \cite{leppanen_serpent_2015}, a 
    continuous-energy Monte Carlo code for numerous reactor physics 
    applications. The group constants relevant for Moltres simulations are
    the various macroscopic neutron cross sections, neutron diffusion
    coefficient, average fission energy, average neutron yield, inverse
    neutron speed, fission spectrum, \gls{DNP} decay constants, and effective
    delayed neutron fractions.
    Using these group constants, Moltres then 
    solves for the flux and temperature based on the neutron diffusion 
    equation coupled with temperature advection due to coolant flow. Transient 
    simulations will establish core fuel temperatures during transients.
    These distributions will give insight into MSFR transient behavior,
    which will help us identify potential safety risks.

@@

	Lithium fluoride (LiF) is the major component of the fuel and blanket
	molten salts used for the \gls{MSFR}. Fissile and fertile isotopes are
	introduced
	into the mixture by mole fractions of 77.5\%LiF-22.5\%AcF$_4$, where
	AcF$_4$ represents actinide fluorides such as uranium and thorium
	fluorides. Table \ref{table:fuelsalt} shows the mole fraction of the
	molecular constituents in the \gls{MSFR} fuel salt.
	The \gls{MSFR} supports various fuel compositions; it can run on the same 
	$^{235}$U-$^{238}$U fuel used in most conventional LWRs. It can also run
	on a
	mixture of fresh and used uranium fuel containing reprocessed TRU
	isotopes \cite{fiorina_investigation_2013}. However, the main configuration
	of the \gls{MSFR} is a breeder reactor running on $^{233}$U-$^{232}$Th
	\cite{merle-lucotte_launching_2011}. Previous studies have reported
	breeding ratios of up to 1.1 on the \gls{MSFR} \cite{fiorina_molten_2013}.

\begin{figure}[t] 
	\centering
	\includegraphics[width=0.48\textwidth]{./figures/MSFR}
	\caption{MSFR reactor design concept \cite{serp_molten_2014}.}
	\label{fig:msfr}
\end{figure}

\begin{table}[t]
	\caption{Specifications of the \gls{MSFR} design \cite{serp_molten_2014}.}
	\begin{tabular}{ l l }
		\hline
		Parameter & Value \\
		\hline
		Thermal/Electric output [MW$_{\text{th}}$/MW$_{\text{e}}$] & 3000 /
		1500 
		\\
		Salt volume [m$^3$] & 18 \\
		Salt fraction in core & 0.5 \\
		Number of circulation loops & 16 \\
		Nominal flow rate [kg s$^{-1}$] & 18500  \\
		Nominal circulation time [s] & 4.0 \\
		Inlet/outlet temperature [K] & 923 / 1023 \\
		Blanket volume [m$^3$] & 7.3\\
		\hline
	\end{tabular}
	\label{table:msfr}
\end{table}

\begin{table}[t]
\centering
\captionsetup{justification=centering}
\caption{Fuel salt composition used for the Serpent simulation.}
\begin{tabular}{rr}
\hline
{Isotope} & {Mole fraction [\%]}\\
\hline
$^7$Li & 29.0\\
$^{19}$F & 62.6\\
$^{232}$Th & 7.40\\
$^{233}$U & 1.00\\
\hline
\end{tabular}
\label{table:fuelsalt}
\end{table}

@@

	Various authors have performed a number of steady state and transient
	multiphysics simulations for the \gls{MSFR}. A paper by Fiorina et al.
	\cite{fiorina_modelling_2014} compares results between coupled models
	developed on the multiphysics code COMSOL and an in-house code developed at
	Delft University of Technology. The models used 2D axisymmetric models of
	the \gls{MSFR} and solved multi-group neutron diffusion equations for the
	neutronics, and they showed good agreement for some of the transient cases
	studied. A more comprehensive 3D model has been developed and studied by
	Aufiero et al. \cite{aufiero_development_2014} using the computional fluid
	dynamics (CFD) toolbox OpenFOAM. Although this model relied on the one
	group neutron diffusion equation, it enabled the study of the full 3D core
	geometry and 3D transient scenarios such as the failure of one of the 16
	pumps in the \gls{MSFR}.

	More recently, a coupled tool, comprising of the thermal-hydraulics code
	TRACE and a multi-group 3D spatial neutronics solver \gls{PARCS}, was
	used to run steady state and transient simulations of the \gls{MSFR}
	\cite{pettersen_coupled_2016}. As \gls{PARCS} only supports conventional
	fuel assembly shapes, the authors approximated the 3D axisymmetric
	cylindrical \gls{MSFR} model with
	hexagonal fuel assemblies. This approach allowed for a 3D model
	simulation of the \gls{MSFR} on a coarse mesh, thus improving on the 2D
	axisymmetric COMSOL/TUDelft models with the benefit of much lower
	computation times in comparison to the CFD-OpenFOAM models. On top of
	steady state simulations, the transient scenarios studied by Pettersen
	include loss of heat sink, pump over-speed,
	over-cooling and loss of flow.

	As Moltres was first developed solely for the purpose of simulating
	\glspl{MSR}, it does not require some of the
	approximations arising from repurposing older codes.
	This paper aims to present Moltres simulation results and safety analysis
	of the \gls{MSFR}, for various fuel compositions through its operational
	lifetime.

@@

	This section describes the overall modelling approach and the codes used
	in this paper. First, the early-life and equilibrium compositions were
	obtained from SCALE/TRITON unit cell depletion calculations by Rykhlevskii
	et al. \cite{rykhlevskii_fuel_2019} Their paper used a unit cell model for
	the modelling
	fuel cycle performance of the \gls{MSFR} and three other fast-spectrum
	\glspl{MSR}. The neutron spectrum and depletion calculations on the unit
	cell SCALE/TRITON models were verified against full core SERPENT models and
	showed very good agreement. We selected the equilibrium composition at
	approximately 43 years after start-up because the TRU vector change
	between each depletion time-step from this moment onwards is less than 3\%
	\cite{rykhlevskii_fuel_2019}. For the early-life composition, it is the 
	resulting fuel composition at 300 days after start-up.

	We performed neutronics calculations on SERPENT using these fuel
	compositions and a truncated, reference \gls{MSFR} core model
	\cite{pettersen_coupled_2016} to generate six-group neutronics data for
	Moltres. Isotopes in the fuel compositions, whose
	neutron cross-section data are not found in the
	JEFF-3.1.2 nuclear data library, were omitted from these calculations
	The energy boundaries for the six neutron groups were adopted from previous
	\gls{MSFR} studies and shown in Table \ref{table:bound}.
	As for the \gls{DNP}, there are eight \gls{DNP} groups implicitly defined
	by the JEFF-3.1.2 nuclear data library.
	The reactor model is a 2D axisymmetric model as shown in
	Figure \ref{fig:reference}. This geometry focuses on the active central
	region of the core. Basing the geometry on the reference model facilitates
	comparisons with previous MSFR studies by various authors
	\cite{fiorina_modelling_2014} \cite{pettersen_coupled_2016} on the
	reference model for code-to-code verification purposes.
	The 2D model is extended into a 3D model in SERPENT by rotating it
	around the central axis to form concentric cylinders. Table
	\ref{table:reactivity} shows the overall temperature reactivity feedback
	coefficients due to the Doppler effect and
	temperature-driven fuel salt expansion. The coefficients were derived by
	applying a least squares best fit on the multiplication factors at
	temperatures from 900 K to 1200 K with 50 K intervals.

\begin{table}[t]
	\centering
	\captionsetup{justification=centering}
	\caption{Neutron energy group upper bounds used in Serpent.}
	\begin{tabular}{ll}
		\hline
		{Group number} & {Upper bound [MeV]}\\
		\hline
		1 & 7.485$\times 10^{-4}$\\
		2 & 5.5308$\times 10^{-3}$\\
		3 & 2.47875$\times 10^{-2}$\\
		4 & 0.4979\\
		5 & 2.2313\\
		6 & 12\\
		\hline
	\end{tabular}
	\label{table:bound}
\end{table}
%
\begin{table}[t]
	\centering
	\captionsetup{justification=centering}
	\caption{Temperature reactivity feedback coefficients.}
	\begin{tabular}{rr}
		\hline
		{Composition} & {$\alpha_T$ [pcm K$^{-1}$]}\\
		\hline
		Start-up & $-7.39 \pm 0.03$\\
		Early-life & $-7.25 \pm 0.03$\\
		Equilibrium & $-6.24 \pm 0.03$\\
		\hline
	\end{tabular}
	\label{table:reactivity}
\end{table}

	Finally, with the group constant data from SERPENT, Moltres
	calculated the resulting coupled neutron spectrum and temperature
	distribution for a given velocity profile in the core, from user-specified
	initial conditions towards steady state, or from steady state in the case
	of an accident scenario. We firther simplified the mesh geometry for
	Moltres from the SERPENT model by omitting the absorber,
	heat exchanger, and reflector regions. This is justified as they have
	negligible contribution towards the neutronics. Instead, a vacuum
	boundary condition was imposed on the outer surface of the blanket region,
	along with 923 K Dirichlet boundary conditions for temperature.
	The 2 cm thick blanket tank structural material was also omitted as its
	inclusion resulted in an extra fine mesh which drastically
	increased computational time. Figure \ref{fig:mesh} shows the Moltres
	\gls{MSFR} mesh.

@@

\begin{figure}[h] 
	\centering
	\includegraphics[width=0.47\textwidth]{./figures/reference}
	\captionsetup{justification=centering}
	\caption{Cross-section of the 2D axisymmetric model used in SERPENT.
	Derived from the 2D axisymmetric reference model of the MSFR
	\cite{pettersen_coupled_2016}. Figure is not drawn to scale.}
	\label{fig:reference}
\end{figure}

@@

	Moltres is an application code developed in the \gls{MOOSE} framework
	\cite{gaston_moose:_2009}. \gls{MOOSE} application codes solve non-linear
	problems through the discretization of \glspl{PDE} on an adaptive coarse
	meshing scheme provided by LibMesh \cite{kirk_libmesh:_2006} and PetSc
	\cite{satish_balay_petsc_2015}. Individual terms of \glspl{PDE} that define
	the physics involved in a system are represented in \gls{MOOSE} (and its
	applications) by kernels. For example, the various terms in the neutron
	diffusion equation such as the diffusion term, time evolution term, etc.
	all have a corresponding physics kernel defined in Moltres. Boundary
	conditions are also handled in a similar fashion. Moltres can solve for an
	arbitrary number of neutronics groups as long as the relevant group
	constants are provided in a Moltres-compatible format.

	As mentioned in the previous Moltres study
	\cite{lindsay_introduction_2018}, the neutronics in Moltres is described by
	the time-independent multi-group neutron diffusion equation as shown in
	Equation \ref{eq1}:
%
\begin{align}
	\frac{1}{v_g} &\frac{\partial \phi_g}{\partial t} - \nabla \cdot D_g \nabla
	\phi_g + \Sigma^r_g \phi_g \nonumber \\ 
	&= \sum^G_{g \neq g'} \Sigma^s_{g' \rightarrow g} \phi_{g'} + \chi^p_g
	\sum^G_{g'=1} (1-\beta) \nu \Sigma^f_{g'} \phi_{g'} + \chi^d_g \sum^I_i
	\lambda_i C_i, \label{eq1}
\end{align}
%
	where
{\small
\begin{align}
	v_g &= \text{average speed of neutrons in group }g \\
	\phi_g &= \text{flux of neutrons in group }g \\
	t &= \text{time} \\
	D_g &= \text{diffusion coefficient of neutrons in group }g \\
	\Sigma^r_g &= \text{macroscopic cross-section for removal of neutrons} 
	\nonumber \\
	&\text{from group }g
\end{align}
%
\begin{align}
	\Sigma^s_{g' \rightarrow g} &= \text{macroscopic cross-section of
	scattering from }g' \text{ to }g \\
	\chi^p_g &= \text{prompt fission spectrum neutrons in group }g \\
	G &= \text{number of discrete neutron groups, }g \\
	\nu &= \text{average number of neutrons produced per fission} \\
	\Sigma^f_{g} &= \text{macroscopic fission cross-section} \nonumber \\
	&\text{for neutron in group }g \\
	\chi^d_g &= \text{delayed fission spectrum neutrons in group }g \\
	I &= \text{number of delayed neutron precursor groups} \\
	\beta &= \text{delayed neutron fraction} \\
	\lambda_i &= \text{average decay constant of delayed neutron} \nonumber \\
	&\text{precursors in precursor group }i \\
	C_i &= \text{concentration of delayed neutron precursors} \nonumber \\
	&\text{in precursor group }i .
\end{align}
}

@@

	Lastly, the governing equation for temperature in the molten salt is given
	as:
%
\begin{align}
	\rho c_{p} \frac{\partial T}{\partial t} + \nabla \cdot \big( \rho
	c_{p} \overrightarrow{u} \cdot T - k \nabla T \big) = Q_s - Q_{hx},
	\label{eq3}
\end{align}
%
	where
{\small
\begin{align}
	\rho &= \text{density of molten salt} \\
	c_{p} &= \text{specific heat capacity of molten salt} \\
	T &= \text{temperature of molten salt} \\
	\overrightarrow{u} &= \text{velocity of molten salt} \\
	k &= \text{thermal conductivity of molten salt} \\
	Q_{hx} &= \text{heat sink},
\end{align}
}
	and the source term $Q_s$ is given as:
%
\begin{align}
Q_s = \sum^G_{g=1} \epsilon_g \Sigma_g^f \phi_g. \label{eq4}
\end{align}
%
\begin{figure}[h] 
	\centering
	\includegraphics[width=0.45\textwidth]{./figures/mesh}
	\captionsetup{justification=centering}
	\caption{Mesh of the 2D axisymmetric model used in Moltres.
	The grey and red regions represent the fuel and blanket salt respectively.}
	\label{fig:mesh}
\end{figure}

>>>>

\title{SAFETY ANALYSIS OF THE MOLTEN SALT FAST REACTOR FUEL COMPOSITION USING
MOLTRES \\~\\~\\~\\}
\author{Sun Myung Park$^{a,b}$, Andrei Rykhlevskii$^a$, and
Kathryn D. Huff$^a$}
\institute{$^a$Dept. of Nuclear, Plasma and Radiological Engineering,
University of Illinois at Urbana-Champaign}
\email{$^b$smpark3@illinois.edu}

\usepackage{graphicx} % allows inclusion of graphics
%\usepackage{booktabs} % nice rules (thick lines) for tables
\usepackage{microtype} % improves typography for PDF
\usepackage{float}
\usepackage{longtable}
\usepackage{xspace}
\usepackage{multirow} 
\usepackage{array}
\setlength{\arrayrulewidth}{.4mm}
\renewcommand{\arraystretch}{1.2}
\usepackage[labelfont=bf]{caption}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{enumitem}
\usepackage{placeins}
\usepackage{siunitx}
%\newcolumntype{c}{>{\hsize=.56\hsize}X}
%\newcolumntype{b}{>{\hsize=.7\hsize}X}
%\newcolumntype{s}{>{\hsize=.74\hsize}X}
%\newcolumntype{f}{>{\hsize=.1\hsize}X}
%\newcolumntype{a}{>{\hsize=.45\hsize}X}
%\usepackage{titlesec}
%\titleformat*{\subsection}{\normalfont}
%\usepackage[super]{cite}
\usepackage{multirow}
\usepackage{hhline}
\usepackage{dcolumn}

@@

\begin{abstract}
%
\textit{
    The Molten
    Salt Fast Reactor (MSFR) has garnered much interest for its inherent
    safety and sustainbility features. The MSFR can adopt a closed thorium fuel
    cycle for
    sustainable operation through the breeding of $^{233}$U from $^{232}$Th.
    The fuel composition changes significantly over the course of its lifespan.
    In this study, we investigated the steady state and transient behavior of
    the MSFR using Moltres, a coupled neutronics/thermal-hydraulics code
    developed within the Multiphysics Object Oriented Simulation Environment
    (MOOSE) framework. Three different fuel compositions, start-up,
    early-life, and equilibrium, were examined for potentially
    dangerous
    core temperature excursions during a unprotected loss of heat sink (ULOHS)
    accident. The six-group and total neutron flux distributions 
    showed good agreement with SERPENT and
    published MSFR results, while the temperature distribution and total power
    showed discrepancies which can be attributed to known sources of error.
    For the transient behavior under the ULOHS
    scenario, while the transition time towards the new steady state core
    temperature is also in good agreement with existing MSFR simulations by
    Fiorina et al., Moltres underestimated the
    temperature rise by a factor of ten, due to the same sources of
    error affecting the steady state results. While an MSFR loaded with
    start-up fuel composition operates at a higher temperature than with the
    other two fuel compositions, all three cases were shown to be inherently
    safe due to the strong negative temperature feedback.
}
\end{abstract}

@@

    We generated group constants for 
    each fuel composition using SERPENT \cite{leppanen_serpent_2015}, a 
    continuous-energy Monte Carlo code for numerous reactor physics 
    applications. The group constants relevant for Moltres simulations are
    the various macroscopic neutron cross sections, neutron diffusion
    coefficient, average fission energy, average neutron yield, inverse
    neutron speed, fission spectrum, \gls{DNP} decay constants, and effective
    delayed neutron fractions.
    Using these group constants, Moltres then 
    solves for the flux and temperature based on the neutron diffusion 
    equation coupled with temperature advection due to coolant flow. Transient 
    simulations will establish core fuel temperatures during transients.
    These distributions will give insight into \gls{MSFR} transient behavior,
    which will help us identify potential safety risks.

\begin{figure}[h] 
	\centering
	\includegraphics[width=0.48\textwidth]{./figures/MSFR}
	\caption{MSFR reactor design concept \cite{serp_molten_2014}.}
	\label{fig:msfr}
\end{figure}

\begin{table}[h]
	\caption{Specifications of the \gls{MSFR} design \cite{serp_molten_2014}.}
	\begin{tabular}{ l l }
		\hline
		Parameter & Value \\
		\hline
		Thermal/Electric output [MW$_{\text{th}}$/MW$_{\text{e}}$] & 3000 /
		1500 
		\\
		Salt volume [m$^3$] & 18 \\
		Salt fraction in core & 0.5 \\
		Number of circulation loops & 16 \\
		Nominal flow rate [kg s$^{-1}$] & 18500  \\
		Nominal circulation time [s] & 4.0 \\
		Inlet/outlet temperature [K] & 923 / 1023 \\
		Blanket volume [m$^3$] & 7.3\\
		\hline
	\end{tabular}
	\label{table:msfr}
\end{table}

\begin{table}[t]
\centering
\captionsetup{justification=centering}
\caption{Fuel salt composition used for the Serpent simulation.}
\begin{tabular}{lS}
\hline
{Isotope} & {Mole fraction [\%]}\\
\hline
$^7$Li & 29.0\\
$^{19}$F & 62.6\\
$^{232}$Th & 7.40\\
$^{233}$U & 1.00\\
\hline
\end{tabular}
\label{table:fuelsalt}
\vspace{.5cm}
	\centering
	\captionsetup{justification=centering}
	\caption{Fuel and blanket salt properties. $T$ denotes temperature in
	Kelvins.}
	{\small
	\begin{tabular}{ll}
		\hline
		{Property} & {Value}\\
		\hline
		Density, $\rho$ [kg m$^{-3}$] & $4983.56 - 0.882 \cdot T$ \\
		Thermal cond. , $k$ [W m$^{-1}$ K$^{-1}$] & $0.928 + 8.397 \times 10
		^{-5} \cdot T$\\
		Specific heat, $c_p$ [J kg$^{-1}$ K$^{-1}$] & $-1111 + 2.78 \cdot T$ \\
		\hline
	\end{tabular}
	}
	\vspace{.5cm}
	\label{table:saltprop}
	\centering
	\captionsetup{justification=centering}
	\caption{Material compositions and densities of the absorber,
	and reflector regions. All elements listed are in their natural
	compositions.}
	{\small
	\begin{tabular}{llSr}
		\hline
		Region & Element & At\% & Density [kg m$^{-3}$]\\
		\hline
		\multirow{2}{*}{Absorber} & B & 80  & \multirow{2}{*}{2520}\\
		& C & 20 & \\
		\hline
		\multirow{4}{*}{Reflector} & Ni & 67.7 & \multirow{4}{*}{10000} \\
		& W & 25.0 & \\
		& Cr & 7.0 & \\
		& Al & 0.3 & \\
		\hline
	\end{tabular}
	}
	\label{table:material}
\end{table}

    Section II provides the specifications and a literature review of the
    \gls{MSFR} concept. Section III covers the overall modeling approach with
    respect to the codes used in this study: SERPENT and Moltres. Section IV
    presents steady state neutron flux and temperature distribution results
    from Moltres for the three different fuel compositions studied. Section V
    explores the \gls{MSFR}'s neutronic and thermodynamic response to a
    \gls{ULOHS} scenario. Lastly, Section VI provides conclusions and
    suggestions for future work.

@@

	Lithium fluoride (LiF) is the major component of the fuel and blanket
	molten salts used for the \gls{MSFR}. Fissile and fertile isotopes are
	introduced
	into the mixture by mole fractions of 77.5\%LiF-22.5\%AcF$_4$, where
	AcF$_4$ represents actinide fluorides such as uranium and thorium
	fluorides. Table \ref{table:fuelsalt} shows the mole fraction of the
	molecular constituents in the \gls{MSFR} fuel salt, with the relevant
	physical properties in Table \ref{table:saltprop}.
	The \gls{MSFR} supports various fuel compositions; it can run on the same 
	$^{235}$U-$^{238}$U fuel used in most conventional LWRs. It can also run
	on a
	mixture of fresh and used uranium fuel containing reprocessed TRU
	isotopes \cite{fiorina_investigation_2013}. However, the main configuration
	of the \gls{MSFR} is a breeder reactor running on $^{233}$U-$^{232}$Th
	\cite{merle-lucotte_launching_2011}. Previous studies have reported
	breeding ratios of up to 1.1 on the \gls{MSFR} \cite{fiorina_molten_2013}.

@@

	Various authors have performed a number of steady state and transient
	multiphysics simulations for the \gls{MSFR}. A paper by Fiorina et al.
	\cite{fiorina_modelling_2014} compares results between models
	developed on the multiphysics software COMSOL, and coupled in-house codes
	developed at
	Delft University of Technology. The models used 2D axisymmetric models of
	the \gls{MSFR} and solved multi-group neutron diffusion equations for the
	neutronics, and they showed good agreement for some of the transient cases
	studied. A more comprehensive 3D model has been developed and studied by
	Aufiero et al. \cite{aufiero_development_2014} using the computional fluid
	dynamics (CFD) toolbox OpenFOAM. Although this model relied on the one
	group neutron diffusion equation, it enabled the study of the full 3D core
	geometry and 3D transient scenarios such as the failure of one of the 16
	pumps in the \gls{MSFR}.

	More recently, a coupled tool, comprising of the thermal-hydraulics code
	TRACE and a multi-group 3D spatial neutronics solver \gls{PARCS}, was
	used to run steady state and transient simulations of the \gls{MSFR}
	\cite{pettersen_coupled_2016}. As \gls{PARCS} only supports conventional
	fuel assembly shapes, the authors approximated the 3D axisymmetric
	cylindrical \gls{MSFR} model with
	hexagonal fuel assemblies. This approach allowed for a 3D model
	simulation of the \gls{MSFR} on a coarse mesh and showed good agreement
	with the COMSOL and TUDelft models with the benefit of much lower
	computation times in comparison to the OpenFOAM CFD model. On top of
	steady state simulations, the transient scenarios studied by Pettersen
	include loss of heat sink, pump over-speed, over-cooling and loss of flow.

	As Moltres is developed on the \gls{MOOSE} framework, it can perform
	implicit multiphysics coupling on an adaptive meshing scheme over multiple
	processing units for accurate and efficient \gls{MSR} simulations.
	This paper aims to present Moltres simulation results and safety analysis
	of the \gls{MSFR}, for various fuel compositions through its operational
	lifetime.

@@

	This section describes the overall modelling approach and the codes used
	in this paper. First, the early-life and equilibrium compositions were
	obtained from SCALE/TRITON unit cell depletion calculations by Rykhlevskii
	et al. \cite{rykhlevskii_fuel_2019} The authors used unit cell
	approximations for the modeling
	fuel cycle performance of the \gls{MSFR} and three other fast-spectrum
	\glspl{MSR}. We selected the equilibrium composition at
	approximately 43 years after start-up because the TRU vector change
	between each depletion time-step from this moment onwards is less than 3\%
	\cite{rykhlevskii_fuel_2019}. For the early-life composition, it is the 
	resulting fuel composition at 300 days after start-up.

	We performed neutronics calculations on SERPENT using these fuel
	compositions and a truncated, reference \gls{MSFR} core model
	\cite{pettersen_coupled_2016} to generate six-group neutronics data for
	Moltres. The material compositions and densities for the absorber,
	and reflector regions are given in Table \ref{table:material}. We set a
	neutron population of 200,000 with 50 inactive cycles and 500 active
	cycles. For
	simplicity, the heat exchanger and pump region were modeled after
	Hastelloy N \cite{hastelloy_2017}. Isotopes in the fuel compositions, whose
	neutron cross-section data are not found in the
	JEFF-3.1.2 nuclear data library, were omitted from these calculations
	The energy boundaries for the six neutron groups were adopted from previous
	\gls{MSFR} studies and shown in Table \ref{table:bound}.
	As for the \gls{DNP}, there are eight \gls{DNP} groups implicitly defined
	by the JEFF-3.1.2 nuclear data library.
	The reactor model is a 2D axisymmetric model as shown in
	Figure \ref{fig:reference}. This geometry focuses on the active central
	region of the core. Basing the geometry on the reference model facilitates
	comparisons with previous MSFR studies by various authors
	\cite{fiorina_modelling_2014} \cite{pettersen_coupled_2016} on the
	reference model for code-to-code verification purposes.
	The 2D model is extended into a 3D model in SERPENT by rotating it
	around the central axis to form concentric cylinders. Table
	\ref{table:reactivity} shows the overall temperature reactivity feedback
	coefficients due to the Doppler effect and
	temperature-driven fuel salt expansion. The coefficients were derived by
	applying a least squares best fit on the multiplication factors at
	temperatures from 900 K to 1200 K with 50 K intervals.

\begin{table}[t]
	\centering
	\captionsetup{justification=centering}
	\caption{Neutron energy group upper bounds used in Serpent.}
	\begin{tabular}{c S}
		\hline
		{Group number} & {Upper bound [MeV]}\\
		\hline
		1 & 7.485$\times 10^{-4}$\\
		2 & 5.5308$\times 10^{-3}$\\
		3 & 2.47875$\times 10^{-2}$\\
		4 & 0.4979\\
		5 & 2.2313\\
		6 & 12\\
		\hline
	\end{tabular}
	\label{table:bound}
	\centering
	\captionsetup{justification=centering}
	\caption{Temperature reactivity feedback coefficients.}
	\begin{tabular}{lr}
		\hline
		{Composition} & {$\alpha_T$ [pcm K$^{-1}$]}\\
		\hline
		Start-up & $-7.39 \pm 0.03$\\
		Early-life & $-7.25 \pm 0.03$\\
		Equilibrium & $-6.24 \pm 0.03$\\
		\hline
	\end{tabular}
	\label{table:reactivity}
\end{table}	
%	
	Finally, with the group constant data from SERPENT, Moltres
	calculated the resulting coupled neutron spectrum and temperature
	distribution for a given velocity profile in the core, from user-specified
	initial conditions towards steady state, or from steady state in the case
	of an accident scenario. We firther simplified the mesh geometry for
	Moltres from the SERPENT model by omitting the absorber,
	heat exchanger, and reflector regions. This is justified as they have
	negligible contribution towards the neutronics. Instead, a vacuum
	boundary condition was imposed on the outer surface of the blanket region,
	along with 923 K Dirichlet boundary conditions for temperature.
	The 2 cm thick blanket tank structural material was also omitted as its
	inclusion resulted in an extra fine mesh which drastically
	increased computational time. Figure \ref{fig:mesh} shows the Moltres
	\gls{MSFR} mesh.

@@

\begin{figure}[t] 
	\centering
	\includegraphics[width=0.47\textwidth]{./figures/reference}
	\captionsetup{justification=centering}
	\caption{Cross-section of the 2D axisymmetric model used in SERPENT.
	Derived from the \gls{MSFR} reference model
	\cite{pettersen_coupled_2016}. Figure is not drawn to scale. All dimensions
	are in cm.}
	\label{fig:reference}
\end{figure}

@@

	Moltres is an application code developed in the \gls{MOOSE} framework
	\cite{gaston_moose:_2009}. \gls{MOOSE} application codes solve non-linear
	problems through the discretization of \glspl{PDE} on an adaptive coarse
	meshing scheme provided by LibMesh \cite{kirk_libmesh:_2006} and PetSc
	\cite{satish_balay_petsc_2015}. Individual terms of \glspl{PDE} that define
	the physics involved in a system are represented in \gls{MOOSE} (and its
	applications) by kernels. For example, the various terms in the neutron
	diffusion equation such as the diffusion term, time evolution term, etc.
	all have a corresponding physics kernel defined in Moltres. Boundary
	conditions are also handled in a similar fashion. Moltres can solve for an
	arbitrary number of neutronics groups as long as the relevant group
	constants are provided in a compatible text format.

	As mentioned in the previous Moltres study
	\cite{lindsay_introduction_2018}, the neutronics in Moltres is described by
	the time-independent multi-group neutron diffusion equation as shown in
	Equation \ref{eq1}:
%
\begin{align}
	\frac{1}{v_g} &\frac{\partial \phi_g}{\partial t} - \nabla \cdot D_g \nabla
	\phi_g + \Sigma^r_g \phi_g \nonumber \\ 
	&= \sum^G_{g \neq g'} \Sigma^s_{g' \rightarrow g} \phi_{g'} + \chi^p_g
	\sum^G_{g'=1} (1-\beta) \nu \Sigma^f_{g'} \phi_{g'} + \chi^d_g \sum^I_i
	\lambda_i C_i, \label{eq1}
\end{align}
%
	where
{\small
\begin{align*}
	v_g &= \text{average speed of neutrons in group }g \\
	\phi_g &= \text{flux of neutrons in group }g \\
	t &= \text{time} \\
	D_g &= \text{diffusion coefficient of neutrons in group }g \\
	\Sigma^r_g &= \text{macroscopic cross-section for removal of neutrons} 
	\nonumber \\
	&\text{from group }g
\end{align*}
%
\begin{align*}
	\Sigma^s_{g' \rightarrow g} &= \text{macroscopic cross-section of
	scattering from }g' \text{ to }g \\
	\chi^p_g &= \text{prompt fission spectrum neutrons in group }g \\
	G &= \text{number of discrete neutron groups, }g \\
	\nu &= \text{average number of neutrons produced per fission} \\
	\Sigma^f_{g} &= \text{macroscopic fission cross-section} \nonumber \\
	&\text{for neutron in group }g \\
	\chi^d_g &= \text{delayed fission spectrum neutrons in group }g \\
	I &= \text{number of delayed neutron precursor groups} \\
	\beta &= \text{delayed neutron fraction} \\
	\lambda_i &= \text{average decay constant of delayed neutron} \nonumber \\
	&\text{precursors in precursor group }i \\
	C_i &= \text{concentration of delayed neutron precursors} \nonumber \\
	&\text{in precursor group }i .
\end{align*}
}

@@

	Lastly, the governing equation for temperature in the molten salt is given
	as:
%
\begin{align}
	\rho c_{p} \frac{\partial T}{\partial t} + \nabla \cdot \big( \rho
	c_{p} \overrightarrow{u} \cdot T - k \nabla T \big) = Q_s - Q_{hx},
	\label{eq3}
\end{align}
%
	where
{\small
\begin{align*}
	\rho &= \text{density of molten salt} \\
	c_{p} &= \text{specific heat capacity of molten salt} \\
	T &= \text{temperature of molten salt} \\
	\overrightarrow{u} &= \text{velocity of molten salt} \\
	k &= \text{thermal conductivity of molten salt} \\
	Q_{hx} &= \text{heat sink},
\end{align*}
}
	and the source term $Q_s$ is given as:
%
\begin{align}
Q_s = \sum^G_{g=1} \epsilon_g \Sigma_g^f \phi_g. \label{eq4}
\end{align}
%
\begin{figure}[h] 
	\centering
	\includegraphics[width=0.45\textwidth]{./figures/mesh}
	\captionsetup{justification=centering}
	\caption{Mesh of the 2D axisymmetric model used in Moltres.
	The grey and red regions represent the fuel and blanket salt respectively.}
	\label{fig:mesh}
\end{figure}
